---
title: "Introduction to the amR package suite"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to the amR package suite}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview
The amR package suite provides tools for antimicrobial resistance (AMR) prediction in bacterial pathogens. It consists of three packages:

- **amRdata**: Data curation and feature extraction from bacterial genomes
- **amRml**: Machine learning models for AMR prediction
- **amRshiny**: Interactive dashboard for exploring results

## Installation

To install all packages in the amR suite:

```{r install, eval = FALSE}
library(amR)
installAMR()
```

This will install amRdata, amRml, and amRshiny from GitHub.

### Installing specific packages

You can also install specific packages:

```{r install-specific, eval = FALSE}
# Install only the ML package
installAMR(packages = "ml")

# Install data and ML packages
installAMR(packages = c("data", "ml"))
```

### Installation options

The `installAMR()` function supports several options:

```{r install-options, eval = FALSE}
# Force reinstall
installAMR(force = TRUE)

# Quiet installation
installAMR(quiet = TRUE)

# Control dependency upgrades
installAMR(upgrade = "never")
```

## Workflow

A typical amR workflow involves:
1. Preparing genomic feature data with **amRdata**
2. Training ML models with **amRml**
3. Exploring results with **amRshiny**

See the individual package vignettes for detailed usage instructions.
